Self Regulation Ontology Retest Analyses

### 2018-05-17 code/SRO_Retest_Analyses.Rmd
frisem prep

```{r}
demog_rel_df %>%
  ggplot(aes(icc))+
  geom_density(fill = 'grey', alpha = 0.7, color = NA)+
  xlab("ICC")+
  ylab("Density")

@@

ggsave('LitReviewSampleSize.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 3, height = 5, units = "in", limitsize = FALSE, dpi = 300)
```

@@

@@

```{r}
ggplotly(rel_comp %>% 
  ggplot(aes(sample_size, retest_reliability, color=task))+
  geom_smooth(method='lm')+
  geom_point(alpha = 0.2)+
  theme(legend.title = element_blank())+
  xlab("Sample Size")+
  ylab("Retest reliability"))

ggsave('LitReviewRelBySampleSize.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 8, height = 5, units = "in", limitsize = FALSE, dpi = 300)
```

>>>>

```{r}
demog_rel_df %>%
  ggplot(aes(icc))+
  geom_histogram(fill = 'grey', alpha = 0.7, color = NA)+
  xlab("ICC")+
  ylab("Count")

@@

ggsave('LitReviewSampleSize.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 3, height = 5, units = "in", limitsize = FALSE, dpi = 500)
```

@@

Are the residuals of this model heteroscedasticity

```{r}
tmp = data.frame(rel_comp$sample_size, resid(mod2)) %>%
  rename(sample_size = rel_comp.sample_size, resid = resid.mod2.)

tmp %>%
  ggplot(aes(sample_size, resid))+
  geom_point()+
  geom_smooth(method = "lm")

summary(lm(resid ~ sample_size, tmp))
```

@@

```{r}
rel_comp %>% 
  ggplot(aes(sample_size, retest_reliability, color=task))+
  geom_smooth(method='lm')+
  # geom_point(alpha = 0.2)+
  theme(legend.title = element_blank(),
        axis.title.y = element_text(size=14),
        axis.title.x = element_text(size=14))+
  xlab("Sample Size")+
  ylab("Retest reliability")+
  ylim(-0.15, 1)

ggsave('LitReviewRelBySampleSize.jpg', device = "jpeg", path = "/Users/zeynepenkavi/Dropbox/PoldrackLab/SRO_Retest_Analyses/output/figures/", width = 8, height = 5, units = "in", limitsize = FALSE, dpi = 500)
```
